{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-10-14 thesis/future.tex
turns out oathbringer had a good quote after all

\chapter{Future Work}
\label{chap:warpzone}
\inspirationalquote{
\begin{tabular}{p{0.75\textwidth}}
We can't be free until we learn to laugh at ourselves.
Once you look in the mirror and see just how foolish we can be,
laughter is inevitable.
And from laughter comes wisdom.
\end{tabular}}
{G'Kar, Babylon 5}

>>>>

\chapter{Future Work}
\label{chap:warpzone}
\inspirationalquote{
	\begin{tabular}{p{0.62\textwidth}}
		"Journey before destination."
		\\
		Some may call it a simple platitude, but it is far more.
		A journey will have pain and failure.
		It is not only the steps forward that we must accept.
		It is the stumbles. The trials. The knowledge that we will fail.
		% That we will hurt those around us.
		\\
		% But
		If we stop, if we accept the person we are when we fall, the journey ends.
		% That failure /becomes/ our destination.
		To love the journey is to accept no such end.
		% I have found, through painful experience,
		% that the most important step a person can take is always the /next/ one.
	\end{tabular}}
%{Galatea, The Talos Principle}
{Dalinar Kholin, Oathbringer}
